NIHAO VII: Predictions for the galactic baryon budget in dwarf to Milky Way mass haloes

### 2016-05-30 ms_nihao_budget.tex
Aaron's edition

%DARK MATTER
\def \rs {\ifmmode r_{\rm s} \else $r_{\rm s}$ \fi} 
\def \rh {\ifmmode r_{\rm h} \else $r_{\rm h}$ \fi} 
\def \Rvir {\ifmmode R_{\rm vir} \else $R_{\rm vir}$ \fi}
\def \Vvir {\ifmmode V_{\rm  vir} \else  $V_{\rm vir}$  \fi} 
\def \Vmax {\ifmmode V_{\rm  max} \else  $V_{\rm max}$  \fi} 
\def \Mvir {\ifmmode M_{\rm  vir} \else $M_{\rm  vir}$ \fi}  
\def \Mhalo {\ifmmode M_{\rm tot} \else $M_{\rm  tot}$ \fi}  
\def \Nvir {\ifmmode N_{\rm  vir} \else $N_{\rm  vir}$ \fi}  
\def \Jvir {\ifmmode J_{\rm vir} \else $J_{\rm vir}$ \fi} 
\def \Evir {\ifmmode E_{\rm vir} \else $E_{\rm vir}$ \fi} 
\def \lam {\ifmmode \lambda  \else $\lambda$ \fi} 
\def \lamp {\ifmmode \lambda^{\prime} \else $\lambda^{\prime}$  \fi} 
\def \lampc {\ifmmode \lambda^{\prime}_{\rm c} \else
  $\lambda^{\prime}_{\rm c}$  \fi}

@@

%%BARYONS
\def \Mb {\ifmmode M_{\rm b} \else $M_{\rm b}$ \fi} 
\def \eSF {\ifmmode \epsilon_{\rm SF} \else $\epsilon_{\rm SF}$ \fi} 
\def \Md {\ifmmode M_{\rm d} \else $M_{\rm d}$ \fi} 
\def \Mg {\ifmmode M_{\rm g} \else $M_{\rm g}$ \fi} 
\def \Rb {\ifmmode R_{\rm b} \else $R_{\rm b}$ \fi} 
\def \Rd {\ifmmode R_{\rm d} \else $R_{\rm d}$ \fi} 
\def \Rg {\ifmmode R_{\rm g} \else $R_{\rm g}$ \fi} 
\def \mgal {\ifmmode m_{\rm gal} \else $m_{\rm gal}$ \fi} 
\def \rj {\ifmmode {\cal R}_j \else ${\cal R}_j$ \fi} 
\def \lamgal {\ifmmode \lambda_{\rm gal} \else $\lambda_{\rm gal}$ \fi} 
\def \Vcirc {\ifmmode V_{\rm circ} \else $V_{\rm circ}$ \fi} 
\def \Vrot {\ifmmode V_{\rm rot} \else $V_{\rm rot}$ \fi} 
\def \Vflat {\ifmmode V_{\rm flat} \else $V_{\rm flat}$ \fi} 
\def \Mstar {\ifmmode M_{\rm star} \else $M_{\rm star}$ \fi} 
\def \Mgas {\ifmmode M_{\rm gas} \else $M_{\rm gas}$ \fi} 
\def \Mbar {\ifmmode M_{\rm bar} \else $M_{\rm bar}$ \fi}

@@

\begin{abstract}
  We use the NIHAO galaxy formation simulations to make predictions
  for the baryonic budget  in present day galaxies ranging from dwarf
  ($\Mhalo\sim10^{10} \Msun$) to Milky Way ($\Mhalo\sim10^{12} \Msun$)
  masses.  The sample is made of 88 independent high resolution
  cosmological zoom-in simulations.  NIHAO galaxies reproduce key
  properties of observed galaxies, such as the stellar mass vs halo
  mass and cold gas vs stellar mass relations. Thus they make
  plausible predictions for the baryon budget.  We present the mass
  fractions of stars, cold gas ($T<10^4$K), cool gas ($10^4 < T <
  10^5$K), warm-hot gas ($10^5 < T < 10^7$K), and hot gas ($10^7$K$ <
  T$), inside the virial radius, $R_{200}$.  Compared to the predicted
  baryon mass, using the dark halo mass and the universal baryon
  fraction, $f_{\rm b}\equiv \Omega_{\rm b}/\Omega_{\rm m}=0.15$, we
  find that for all of our haloes, the missing mass is not just outside 
  the virial radius $\Rvir$, it has been relocated past 2$\Rvir$.  
  Haloes of mass $\Mhalo\sim 10^{10}\Msun$ are missing $\sim
  90\%$ of their baryons.  More massive haloes ($\Mhalo\sim
  10^{12}\Msun$) retain a higher fraction of their baryons, with $\sim
  30\%$ missing, consistent with observational estimates.    
%  Finally we show that the baryonic budget of most massive 
%  galaxies in NIHAO suite can match the observation for most 
%  components but the cool gas, which requires further 
%  theoretical and observational work to find the answer where
%  the cool gas actually is.
\end{abstract}

@@

%% missing baryon problem
On cosmological scales, the ratio between the total baryonic and
gravitating mass is measured to be $f_{\rm b}\equiv \Omega_{\rm
  b}/\Omega_{\rm m}\simeq 0.16$ (The Planck Collaboration 2014).
However, the cold baryonic mass density implied by several galaxy baryon
estimates is only 3-8\% of the big bang nucleosynthesis expection
\citep{Persic92, Fukugita98,  Bell03, McGaugh10}.  The majority of the
cosmic baryons are thought to be in the form of hot gas around or
between galaxies \citep{Cen09}. Until recently only a fraction of
these baryons had been detected \citep{Bregman07, Shull12}.  This
discrepancy is referred to as the ``missing baryon problem''.
Recent advances in the detection of gas in the circum
galactic medium (CGM) have come from the COS survey \citep{Tumlinson11,
  Tumlinson13, Thom12,  Werk12, Werk13}.  On the scale of Milky Way
mass haloes $\Mhalo \sim 10^{12}\Msun$ a significant amount of warm
($10^4 < T < 10^7$K) gas has been detected \citep{Werk14}, accounting
for 33-88\% of the baryon budget. In the future such observations will
be extended to a wider range of halo masses.

In this paper we make predictions for the baryonic budget for stars,
cold, warm and hot gas in and around the virial radius of haloes of
mass ranging from $\Mhalo\sim 10^{10}\Msun$ to $10^{12}\Msun$. We use
a sample of 88 zoom-in galaxy formation simulations from the NIHAO
project. NIHAO galaxies are consistent with the stellar mass vs halo
mass relations from halo abundance matching since redshift $z\sim 4$
\citep{Wang15}, the galaxy star formation rate vs stellar mass
relation since $z\sim 4$ \citep{Wang15}, and the cold gas mass vs
stellar mass relation at $z\sim 0$ (Stinson \etal 2015).  Therefore,
the simulations make plausible predictions for the mass fractions and
physical locations of the warm and hot gas components.  We find that
all the haloes contain less baryons than expected according to the
cosmic baryonic fraction, but the missing fraction is strongly mass
dependent.

@@

%% FIGURE 1
\begin{figure}
\centerline{
%  \psfig{figure=barbudget_linear_v3.eps,width=0.5\textwidth}}
%\centerline{
%  \psfig{figure=barbudget_v3.eps,width=0.5\textwidth}
  \psfig{figure=barbudget_linearlog.eps,width=0.5\textwidth}
}
\caption{Fractional baryon content of our NIHAO simulations 
  as a function of halo
  mass. The green points show the ratio between the baryonic mass
  (stars + gas) inside the virial radius and the total baryonic mass
  associated with the dark matter halo and the green lines are best
  fitting lines. The blue points show the
  corresponding fraction for the stars. The solid green line and
  shaded region shows a double power-law fit, together with the
  1$\sigma$ scatter. For the stellar mass fraction we show several
  relations from halo abundance matching.    The linear (upper panel)
  and logarithmic (lower panel) scales emphasize the large amount of
  ``missing'' baryons and the low star formation efficiencies.}
\label{fig:budget}
\end{figure}

%% FIGURE 2
\begin{figure*}
\centerline{
  \psfig{figure=budgetpro.eps,width=0.99\textwidth}
}
\caption{Radial profile of the mass fraction of the gas in each phase
         to total baryon mass in each radial bin 
         at z=0 for all galaxies in NIHAO sample.
         Each solid line is from one galaxy and color coded with
         the halo mass.}
\label{fig:corona}
\end{figure*}

%% FIGURE 3
\begin{figure}
\centerline{
  \psfig{figure=ratioprofile_v4.eps,width=0.5\textwidth}
}
\caption{Baryon distribution of each galaxy from NIHAO simulations.
  A comparison of how the baryons distribute in the halo with 
  different masses. 
  The lines are color coded by their halo mass, which show a clear
  trend that the more massive halo preserve more baryons alone
  the radius.}
\label{fig:rps}
\end{figure}

@@

We tried to capture the behaviour of the baryonic mass fraction as a 
function of the halo mass using a double power law formula:
\begin{equation}
\frac{f}{f_0} = \left( 
                        \frac{M_{200}}{\mathcal{M}_0} 
                        \right)^\alpha 
                        \left\{ 0.5 \left[ 1+\left( 
                        \frac{M_{200}}{\mathcal{M}_0} 
                        \right)^\gamma \right] 
                        \right\}^{\frac{\beta-\alpha}{\gamma}}.
\end{equation}
In this formula, the lower and higher mass ends have logarithmic slope
$\alpha$ and $\beta$, respectively, while $\gamma$ regulates how 
sharp the transition is from the lower to the higher ends.
The best fit parameters are as follows:
\begin{eqnarray}
\mathcal{M}_0  &=&  6.76 \times 10^{10} \nonumber \\
f_0  &=&   0.336 \nonumber \\
\alpha  &=&   0.684 \\
\beta  &=&   0.205 \nonumber \\
\gamma  &=&   3.40\nonumber  
\end{eqnarray}
The green shaded region indicates the scatter about the best fit line,
{\bf which are 0.151 for haloes with mass in the range of  
$3\times 10^{9}\Msun < M_{200} <2\times 10^{10} \Msun$, 0.236 for
halo mass in 
$2\times 10^{10}\Msun < M_{200} < 7\times 10^{10} \Msun$,
0.125 for halo mass in
$7\times 10^{10}\Msun < M_{200} < 3\times 10^{11} \Msun$
and 0.0518 for halo mass in
$3\times 10^{11}\Msun < M_{200} < 3.5\times 10^{12} \Msun$.}

@@

Fig.~\ref{fig:budget} shows that all haloes in our study contain
less than the universal fraction of baryons. The
upper panel uses a linear y-axis scale, which highlights the large
amount of baryons that are missing, especially in low mass haloes. The
logarithmic scale in the lower panel highlights the power-law nature of the relatons.

@@

In Fig.~\ref{fig:corona}, we present the radial distribution of 
gas in different phases normalized to the

@@

%% FIGURE 4
\begin{figure}
\centerline{
  \psfig{figure=budget.eps,width=0.5\textwidth}
}
\caption{Baryonic budget (the fraction of different components) 
  of $3.5\times 10^{11} < M_{200}/\Msun <
  3.5 \times 10^{12}$ NIHAO galaxies (blue points 
  with 1$\sigma$ error bars) compared with observations of 
  M$_{200}$ = 10$^{12.2}$ $\Msun$ galaxies (shaded regions)
  }
\label{fig:comparison}
\end{figure}

%% TABLE 1
\begin{table*}
\caption{The baryonic budget parameters for galaxies in NIHAO sample
  in different mass bins. We refer to gas in the temperature range  T
  $<$ $10^4$ K as cold; $10^4$ K $\leqslant$ T $<$ $10^5$ K as cool;
  $10^5$ K $\leqslant$ T $<$ $10^7$ K as warm;  and T $\geqslant$
  $10^7$ K as hot.}
\begin{center}
\begin{tabular}{ccccc}
\hline
\input{budgettable4.txt}
\hline
\end{tabular}
\label{tab:comperison}
\end{center}
\end{table*}

\subsection{Comparison with Observations of Milky Way mass haloes}
Since the CGM is too diffuse to create emission lines, it must be
observed using quasar absorption lines.
The COS-HALOs survey is filling in details about the $z \sim 0$
CGM \citep{Peeples14, Tumlinson11, Tumlinson13, Werk12, Werk13, Werk14}.
For the CGM of low-redshift $L^*$ galaxies, \citet{Tumlinson13} and 
\citet{Peeples14} constrain the mass of  the
warm-hot CGM ($T \sim 10^{5-7}$), \citet{Werk14} provides a strict
lower limit to the mass of cool material ($T \sim 10^{4-5}$) in the
CGM of these galaxies.  In a study using X-rays, 
\citet{Anderson13} place a
constraints on the mass of  hot gas ($T > 10^7$) residing in the
extended hot halos.

@@

The observations and the simulations match well in every phase
outside of the cool CGM gas, where the observations find $3\times$
the mass that simulations predict.  If the observations are correct,
the simulations have either ejected too far gas that could be cool, or 
they have created a CGM with the wrong mix of gas temperatures. The
total gas fractions (0.39 in COS-HALOs, 0.41 in NIHAO) suggest the
latter option.  As the CGM of lower mass galaxies will soon be observed ,
Table~\ref{tab:comperison} lists information about CGM
mass fractions of the different components of gas in haloes down to a
halo mass of $\sim 10^{10}\Msun$.

@@

\begin{itemize}
\item All of the NIHAO haloes have a lower baryon to dark matter ratio, 
      inside the viriral radius, than the cosmic baryon fraction.

@@

@@

\item For the highest mass haloes in our study $\sim 10^{12}\Msun$ 
      our simulations are consistent with the observed fractions of stars, 
      cold gas, warm and hot gas. However, we underpredict 
      the cool ($10^4 < T < 10^5 K$) gas with $f_{\rm cool}=0.11\pm0.06$ 
      vs 0.28-0.48 observed.

\item This discrepancy may indicate that our feedback model pushes the 
      gas too far, or puts gas in the wrong phases, 
      and can be resolved with future observations. 
      Since we match the overall gas fraction we think that  
      there might be some problem in mixing the gas temperature.
\end{itemize}

@@

% Multiscale Gaussian Random Fields and Their Application to Cosmological Simulations
%\bibitem[Bertschinger(2001)]{Bertschinger01} Bertschinger, E.\ 2001, 
%\apjs, 137, 1

@@

@@

% Dark MaGICC: the effect of dark energy on disc galaxy formation. Cosmology does matter
%\bibitem[Penzo et al.(2014)]{Penzo14} Penzo, C., Macci{\`o}, 
%  A.~V., Casarini, L., Stinson, G.~S., \& Wadsley, J.\ 2014, \mnras, 442, 176

@@

%Evolution of the Mass-Metallicity Relations in Passive and Star-forming Galaxies from SPH-cosmological Simulations

>>>>

%DARK MATTER
\def \rs {\ifmmode r_{\rm s} \else $r_{\rm s}$ \fi} 
\def \rh {\ifmmode r_{\rm h} \else $r_{\rm h}$ \fi} 
\def \Rvir {\ifmmode R_{\rm vir} \else $R_{\rm vir}$ \fi}
\def \Vvir {\ifmmode V_{\rm  vir} \else  $V_{\rm vir}$  \fi} 
\def \Vmax {\ifmmode V_{\rm  max} \else  $V_{\rm max}$  \fi} 
\def \Mvir {\ifmmode M_{\rm  vir} \else $M_{\rm  vir}$ \fi}  
\def \Mhalo {\ifmmode M_{200} \else $M_{200}$ \fi}  
\def \Nvir {\ifmmode N_{\rm  vir} \else $N_{\rm  vir}$ \fi}  
\def \Jvir {\ifmmode J_{\rm vir} \else $J_{\rm vir}$ \fi} 
\def \Evir {\ifmmode E_{\rm vir} \else $E_{\rm vir}$ \fi} 
\def \lam {\ifmmode \lambda  \else $\lambda$ \fi} 
\def \lamp {\ifmmode \lambda^{\prime} \else $\lambda^{\prime}$  \fi} 
\def \lampc {\ifmmode \lambda^{\prime}_{\rm c} \else
  $\lambda^{\prime}_{\rm c}$  \fi}

@@

%%BARYONS
\def \Mb {\ifmmode M_{\rm b} \else $M_{\rm b}$ \fi} 
\def \eSF {\ifmmode \epsilon_{\rm SF} \else $\epsilon_{\rm SF}$ \fi} 
\def \Md {\ifmmode M_{\rm d} \else $M_{\rm d}$ \fi} 
\def \Mg {\ifmmode M_{\rm g} \else $M_{\rm g}$ \fi} 
\def \Rb {\ifmmode R_{\rm b} \else $R_{\rm b}$ \fi} 
\def \Rd {\ifmmode R_{\rm d} \else $R_{\rm d}$ \fi} 
\def \Rg {\ifmmode R_{\rm g} \else $R_{\rm g}$ \fi} 
\def \mgal {\ifmmode m_{\rm gal} \else $m_{\rm gal}$ \fi} 
\def \rj {\ifmmode {\cal R}_j \else ${\cal R}_j$ \fi} 
\def \lamgal {\ifmmode \lambda_{\rm gal} \else $\lambda_{\rm gal}$ \fi} 
\def \Vcirc {\ifmmode V_{\rm circ} \else $V_{\rm circ}$ \fi} 
\def \Vrot {\ifmmode V_{\rm rot} \else $V_{\rm rot}$ \fi} 
\def \Vflat {\ifmmode V_{\rm flat} \else $V_{\rm flat}$ \fi} 
\def \Mstar {\ifmmode M_{\rm star} \else $M_{\rm star}$ \fi} 
\def \Mgas {\ifmmode M_{\rm gas} \else $M_{\rm gas}$ \fi} 
\def \Mbar {\ifmmode M_{\rm bar} \else $M_{\rm bar}$ \fi}
\def \Rbar {\ifmmode R_{\rm bar} \else $R_{\rm bar}$ \fi}

@@

\begin{abstract}
  We use the NIHAO galaxy formation simulations to make predictions
  for the baryonic budget  in present day galaxies ranging from dwarf
  ($\Mhalo\sim10^{10} \Msun$) to Milky Way ($\Mhalo\sim10^{12} \Msun$)
  masses.  The sample is made of 88 independent high resolution
  cosmological zoom-in simulations.  NIHAO galaxies reproduce key
  properties of observed galaxies, such as the stellar mass vs halo
  mass and cold gas vs stellar mass relations. Thus they make
  plausible predictions for the baryon budget.  We present the mass
  fractions of stars, cold gas ($T<10^4$K), cool gas ($10^4 < T <
  10^5$K), warm-hot gas ($10^5 < T < 10^7$K), and hot gas ($10^7$K$ <
  T$), inside the virial radius, $R_{200}$.  Compared to the predicted
  baryon mass, using the dark halo mass and the universal baryon
  fraction, $f_{\rm b}\equiv \Omega_{\rm b}/\Omega_{\rm m}=0.15$, we
  find that all of our haloes {\bf are missing baryons. The missing
    mass been relocated past 2 virial radii, and is dominated by cool gas.}
   Haloes of mass $\Mhalo\sim 10^{10}\Msun$ are missing
  $\sim 90\%$ of their baryons.  More massive haloes ($\Mhalo\sim
  10^{12}\Msun$) retain a higher fraction of their baryons, with $\sim
  30\%$ missing, consistent with observational estimates.

%  Finally we show that the baryonic budget of most massive 
%  galaxies in NIHAO suite can match the observation for most 
%  components but the cool gas, which requires further 
%  theoretical and observational work to find the answer where
%  the cool gas actually is.
\end{abstract}

@@

%% missing baryon problem
On cosmological scales, the ratio between the total baryonic and
gravitating mass is measured to be $f_{\rm b}\equiv \Omega_{\rm
  b}/\Omega_{\rm m}\simeq 0.15$ (The Planck Collaboration 2014).
However, the cold baryonic mass density implied by several galaxy baryon
estimates is only 3-8\% of the big bang nucleosynthesis expectation
\citep{Persic92, Fukugita98,  Bell03, McGaugh10}.  The majority of the
cosmic baryons are thought to be in the form of hot gas around or
between galaxies \citep{Cen09}. Until recently only a fraction of
these baryons had been detected \citep{Bregman07, Shull12}.  This
discrepancy is referred to as the ``missing baryon problem''.
{\bf Several theoretical studies with cosmological simulations
have constrained the phase and cosmological environments of
the potential reservoirs of the missing baryons 
\citep{Yoshida05, He05, Dave10, Zhu11, Haider16}.}

{\bf The circum galactic medium (CGM) is a major potential  reservoir
  of the missing baryons.}  Recent advances in the detection of  gas
in the CGM have come  from the COS survey \citep{Tumlinson11,
  Tumlinson13, Thom12,  Werk12, Werk13}.  On the scale of Milky Way
mass haloes $\Mhalo \sim 10^{12}\Msun$ a significant amount of warm
($10^4 < T < 10^7$K) gas has been detected \citep{Werk14}, accounting
for 33-88\% of the baryon budget. In the future such observations will
be extended to a wider range of halo masses.
%{\bf ??? To understand
%  the physical properties of the CGM and the origins of components in
%  each phase has been shown to be able to test the impact of feedback
%  models \citep{Sharma12,Marasco13}???
  {\bf The physical properties of the CGM has been shown to be able to
    test feedback models \citep{Sharma12,Marasco13}.  \citet{Dave09}
    predicted galactic halo baryon fractions of galaxies with halo
    masses ranging from $10^{11} \Msun$ to $10^{13} \Msun$ using
    cosmological hydrodynamical simulations with a well-constrained
    model for galactic outflows.  They found that, without the outflow
    model, the baryon fraction inside the virial radius is roughly the
    cosmic baryonic fraction, but with the outflow model, the baryon
    fraction is increasingly suppressed in lower mass haloes.  By
    comparing results at $z=3$ and $z=0$, they showed that large
    haloes remove their baryons at early times while small haloes lose
    baryons more recently due to the wind material taking longer to
    return to low-mass galaxies than high-mass galaxies.
%  
  \citet{Sokolowska16} studied the halo gas of three Milky way-sized
  galaxies using cosmological zoom-in simulations. They found that
  most of missing baryons actually resides in warm-hot and hot gas
  which contribute to 80\% of the total gas reservoir.  The recovered
  baryon fraction within 3 virial radii is 90\%.  The warm-hot medium
  is sensitive to the feedback model so that a reliable spatial
  mapping of the warm-hot medium will provide  a stringent test for
  feedback models.}

In this paper we make predictions for the baryonic budget for stars,
cold, warm and hot gas in and around the virial radius of haloes of
mass ranging from $\Mhalo\sim 10^{10}\Msun$ to $10^{12}\Msun$. We use
a sample of 88 zoom-in galaxy formation simulations from the NIHAO
project. NIHAO galaxies are consistent with the stellar mass vs halo
mass relations from halo abundance matching since redshift $z\sim 4$
\citep{Wang15}, the galaxy star formation rate vs stellar mass
relation since $z\sim 4$ \citep{Wang15}, and the cold gas mass vs
stellar mass relation at $z\sim 0$ \citep{Stinson15}.  Therefore,
the simulations make plausible predictions for the mass fractions and
physical locations of the warm and hot gas components.  We find that
all the haloes contain less baryons than expected according to the
cosmic baryonic fraction, but the missing fraction is strongly mass
dependent.  {\bf Mention Gutcke et al. 2016}

@@

%% FIGURE 1
\begin{figure}
\centerline{
%  \psfig{figure=barbudget_linear_v3.eps,width=0.5\textwidth}}
%\centerline{
%  \psfig{figure=barbudget_v3.eps,width=0.5\textwidth}
  \psfig{figure=barbudget_linearlog.eps,width=0.5\textwidth}
}
\caption{Fractional baryon content of our NIHAO simulations  as a
  function of halo mass. The green points show the ratio between the
  baryonic mass (stars + gas) inside the virial radius and the total
  baryonic mass associated with the dark matter halo. The blue points
  show the corresponding fraction for the stars. The solid green line
  and shaded region shows a double power-law fit, together with the
  1$\sigma$ scatter. For the stellar mass fraction we show several
  relations from halo abundance matching.    The linear (upper panel)
  and logarithmic (lower panel) scales emphasize the large amount of
  ``missing'' baryons and the low star formation efficiencies.}
\label{fig:budget}
\end{figure}

%% FIGURE 2
\begin{figure*}
\centerline{
  \psfig{figure=budgetpro.eps,width=0.99\textwidth}
}
\caption{Radial profile of the mass fraction of the gas in each phase
         to total baryon mass in each radial bin 
         at z=0 for all galaxies in NIHAO sample.
         Each solid line is from one galaxy and color coded with
         the halo mass. {\bf tickmarks overlap. fix. use $R_{200}$ for virial radius}}
\label{fig:corona}
\end{figure*}

@@

We tried to capture the behavior of the baryonic mass fraction as a 
function of the halo mass using a double power law formula:
\begin{equation}
\frac{f}{f_0} = \left( 
                        \frac{M_{200}}{\mathcal{M}_0} 
                        \right)^\alpha 
                        \left\{ 0.5 \left[ 1+\left( 
                        \frac{M_{200}}{\mathcal{M}_0} 
                        \right)^\gamma \right] 
                        \right\}^{\frac{\beta-\alpha}{\gamma}}.
\end{equation}
In this formula, the lower and higher mass ends have logarithmic slope
$\alpha$ and $\beta$, respectively, while $\gamma$ regulates how 
sharp the transition is from the lower to the higher ends.
The best fit parameters are as follows:
\begin{eqnarray}
\mathcal{M}_0  &=&  6.76 \times 10^{10} \nonumber \\
f_0  &=&   0.336 \nonumber \\
\alpha  &=&   0.684 \\
\beta  &=&   0.205 \nonumber \\
\gamma  &=&   3.40\nonumber  
\end{eqnarray}
The green shaded region indicates the scatter about the best fit line,
{\bf which is 0.151 for haloes with mass in the range of  
$3\times 10^{9}\Msun < M_{200} <2\times 10^{10} \Msun$, 0.236 for
halo mass in 
$2\times 10^{10}\Msun < M_{200} < 7\times 10^{10} \Msun$,
0.125 for halo mass in
$7\times 10^{10}\Msun < M_{200} < 3\times 10^{11} \Msun$
and 0.0518 for halo mass in
$3\times 10^{11}\Msun < M_{200} < 3.5\times 10^{12} \Msun$.}

@@

Fig.~\ref{fig:budget} shows that all haloes in our study contain less
than the universal fraction of baryons. The upper panel uses a linear
y-axis scale, which highlights the large amount of baryons that are
missing, especially in low mass haloes. The logarithmic scale in the
lower panel highlights the power-law nature of the relations.

@@

{\bf In Fig.~\ref{fig:corona}, we present the radial distribution of
  gas in different phases at $z=0$, normalized to the total baryon
  mass profile, such that for a given halo the four phases add up to
  unity.  All simulations share a common attribute.  The cold gas (T$<
  10^4$ K) is mostly located  near the center  ($R < 0.2 R_{200}$)
  where most stars in galaxies form.  In contrast, the cool ($10^4$K
  $<$ T $<$ $10^5$K) and  warm-hot ($10^5$K $<$ T $<$ $10^7$K) gas are
  located at large distances with roughly constant fractions up to 2
  times $R_{200}$.  The hot gas (T$>10^7$K) is a minority component
  for all galaxies in the NIHAO sample, with the maximum hot gas
  fraction at any radius being  less than 5\%.}

{\bf Despite these similarities, we find a considerably higher proportion
  of cool gas in lower mass galaxies (M$_{\rm tot} < 10^{11} \Msun$)
  in the whole corona region.  For higher mass galaxies, warm-hot gas
  dominates the corona  which signals higher efficiency  of feedback.
  Even beyond the virial radius, the cool and warm-hot gas has similar
  features as the gas within virial radius which reveals the gas
  surrounding galaxies within large distance is the major reservoir of
  baryons.}

%% FIGURE 3
\begin{figure}
\centerline{
  \psfig{figure=ratioprofile_v4.eps,width=0.5\textwidth}
}
\caption{Baryon distribution of each galaxy from NIHAO simulations. 
 The lines are color coded by their halo mass, which shows a
  clear trend that the more massive haloes preserve more baryons at
  all radii.}
\label{fig:rps}
\end{figure}

%% FIGURE 4
\begin{figure}
\centerline{
  \psfig{figure=missing_vr.eps,width=0.5\textwidth}
}
\caption{Baryon radius as function of total virial mass.
         The points are color coded by the ratio 
         between baryon radius and the virial radius of each galaxy.}
\label{fig:missvr}
\end{figure}

%% FIGURE 5
\begin{figure*}
\centerline{
  \psfig{figure=budget_inout.eps,width=0.99\textwidth}
}
\caption{Mass fraction of gas in four phases (relative to the fiducial
  baryonic mass within virial radius). The blue and red points are for
  gas  inside and outside the virial radius, respectively. Cool gas is
  the dominant component of the CGM in NIHAO simulations.}
\label{fig:inout}
\end{figure*}

@@

{\bf To estimate how far the baryons escape, we measured the radius,
  $\Rbar$, within which the total baryon mass equals to the fiducial
  baryonic mass defined by Eq.~\ref{equ:mb}. This is a lower limit to
  the true extent of the missing baryons since the baryon mass
  includes gas and stars that belong to nearby lower mass haloes.
  Fig.~\ref{fig:missvr} shows the baryon radius of each galaxy as
  function of the virial mass.  We find the baryon radius generally
  increases with virial mass. But when normalized by the virial
  radius, the distance baryons are ejected to span a similar range of radii
  $\Rbar/R_{200}\sim 2-6$.}

{\bf In Fig.~\ref{fig:inout}, we calculate the fractions of gas (in each phase)
inside the virial radius (blue points) and between 
the virial and baryon radii (red points).
%
The upper-left panel shows the  fractions of cold gas. The fractions
of cold gas between the virial radius and baryon radius of galaxies with
halo masses in the range between $10^{9} \Msun$ to  $10^{10} \Msun$
are greater than 80\%. As the halo mass increases, this fraction goes
down dramatically, in the mass range between $10^{10} \Msun$ and
$10^{11} \Msun$ the fractions are less than  20\% for most of galaxies
and the fractions for galaxies with halo mass above $10^{11} \Msun$ are
almost 0.  For the cold gas inside the virial radius, the fractions
increase gradually as halo mass increases and the maximum fraction is
about 20\% with at a halo mass of $10^{12} \Msun$.
%
The upper-right panel shows the fractions of cool gas.  The fractions
of cool gas in region outside of virial radius  increase from 0 at
halo masses are $10^9 \Msun$ to 80\% at halo  masses are around
$10^{10} \Msun$ to $10^{11} \Msun$, then  decrease in higher mass
range and reach 0 again at halo masses are $10^{12} \Msun$. The cool
gas inside virial radius shares  a similar trend but the maximum
fraction is about 40\% at  halo masses are $10^{11} \Msun$.
%
The fractions for warm-hot gas are shown in the lower-left panel.
The trends of the gas inside and outside gas are quite similar
which increase as the halo masses increase monotonically and whose 
maximum values are only 20\%.
%
The hot gas shown in the lower-right panel and is negligible both
inside and outside the virial radius across the whole mass range we
study.
%
We thus conclude that, for galaxies with halo mass 
below $10^{11}$, the majority of baryons associated with the
dark matter halo are in the cold and cool phases, 
and are located well outside of virial radius. For the gas inside
virial radius, the majority is cool gas for the galaxies with
halo masses are $10^{11} \Msun$ and when halo masses are higher
than $10^{11} \Msun$ the fractions of cold gas, cool gas and 
warm-hot gas are comparable.}

%% FIGURE 6
\begin{figure}
\centerline{
  \psfig{figure=budget.eps,width=0.5\textwidth}
}
\caption{Baryonic budget 
  of NIHAO haloes of mass $3.5\times 10^{11} < M_{200}/\Msun <
  3.5 \times 10^{12}$ (blue points 
  with 1$\sigma$ error bars) compared with observations of 
  $M_{200} \sim 10^{12}\Msun$ haloes (shaded regions)
  }
\label{fig:comparison}
\end{figure}

%% TABLE 1
\begin{table*}
  \caption{The baryonic budget parameters for NIHAO galaxies
    in different halo  mass bins. We refer to gas in the temperature range  T
  $<$ $10^4$ K as cold; $10^4$ K $\leqslant$ T $<$ $10^5$ K as cool;
  $10^5$ K $\leqslant$ T $<$ $10^7$ K as warm;  and T $\geqslant$
  $10^7$ K as hot.}
\begin{center}
\begin{tabular}{ccccc}
\hline
\input{budgettable4.txt}
\hline
\end{tabular}
\label{tab:comparison}
\end{center}
\end{table*}

\subsection{Comparison with Observations of Milky Way mass haloes}
Since the CGM is too diffuse to create emission lines, it must be
observed using quasar absorption lines.  The COS-HALOs survey is
filling in details about the $z \sim 0$ CGM \citep{Peeples14,
  Tumlinson11, Tumlinson13, Werk12, Werk13, Werk14}.  For the CGM of
low-redshift $\sim L^*$ galaxies ($\Mstar\sim 10^{10.5}\Msun$),
\citet{Tumlinson13} and \citet{Peeples14} constrain the mass of  the
warm-hot CGM ($T \sim 10^{5-7}$K), \citet{Werk14} provides a strict
lower limit to the mass of cool material ($T \sim 10^{4-5}$K) in the
CGM of these galaxies.  In a study using X-rays,  \citet{Anderson13}
place a constraints on the mass of  hot gas ($T > 10^7$K) residing in
the extended hot halos.

@@

The observations and the simulations match well in every phase {\bf
  except} the cool CGM gas, where the observations find $3\times$ the
mass that simulations predict.  If the observations are correct, the
simulations have either ejected {\bf cool gas too far}, or  they have
created a CGM with the wrong mix of gas temperatures. The total gas
fractions (0.39 in COS-HALOs, 0.41 in NIHAO) suggest the latter
option.   {\bf However, \citet{Stern16} developed a new method to
  constrain the physical conditions in the cool CGM from measurements
  of ionic  columns densities. This new method combines the
  information available from different ??? during the photoionization
  modeling, and was applied to the COS-HALOs data,  yielding a total
  cool CGM mass within the virial radius of $1.3\times10^{10}\Msun$
  which is shown by the green hashed bar in Fig~\ref{fig:budget} and
  is in good agreement with our prediction.  As the
  Fig.~\ref{fig:corona} and Fig.~\ref{fig:inout} show, the cool gas is
  the most important component in CGM so that the more accurate
  knowledge of the physical properties of CGM are necessary to better
  understand the role of the CGM in galaxy formation.}
%
As the CGM of lower mass galaxies will soon be observed,
Table~\ref{tab:comparison} lists information about CGM
mass fractions of the different components of gas in haloes down to a
halo mass of $\sim 10^{10}\Msun$.

@@

\begin{itemize}
\item All of the NIHAO haloes have a lower baryon to dark matter ratio, 
      inside the virial radius, than the cosmic baryon fraction.

\item {\bf Cold gas ($T<10^4$K) is mostly restricted to be within
      0.2 virial radii.  The cool gas ($10^4 < T < 10^5$K) dominates
      the corona at low masses ($M_{200}\lta 3\times 10^{11} \Msun$)
      while the warm-hot gas ($10^5 < T < 10^7$K) dominates at high
      masses ($M_{200}\gta 3\times 10^{11} \Msun$).}

@@

\item {\bf ??? I don't understand this sentence ?? Cool gas is a major
  component in total baryons  whose mass is same as the fiducial
  baryonic mass of  total dark matter mass inside virial radius. Most
  of the cool gas in these baryons locates out of the virial radius.}

@@

\item For the highest mass haloes in our study $\sim 10^{12}\Msun$ our
      simulations are consistent with the observed  fractions of stars,
      cold gas, warm and hot gas.

\item {\bf For the cool gas we predict $f_{\rm cool}=0.11\pm0.06$
      which is significantly lower than the observations from COS-HALOs
      ($f_{\rm cool}=0.28-0.48$), but is in excellent agreement with the
      analysis of \citet{Stern16}.}

\end{itemize}

@@

@@

% Missing Halo Baryons and Galactic Outflows
\bibitem[Dav{\'e} (2009)]{Dave09} Dav{\'e}, R.\ 2009, ASPC, 419, 347D

% The intergalactic medium over the last 10 billion years - I. Lya absorption and physical conditions
\bibitem[Dav{\'e} et al.(2010)]{Dave10} Dav{\'e}, R., Oppenheimer, B.~D., Katz, N., et al.\ 2010, \mnras, 408, 2051

@@

@@
